Target Markdown

### 2023-04-14 _targets.Rmd
small changes
small edits

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt"
                            ))

@@

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
    #  tar_target(all_pubs,
    #        get_all_pubs(db_path, matching, ids_complete), 
    #           format = "qs"),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector))

@@

   # tar_target(topic_model_input,
   #            make_topic_model_input(all_pubs)) #,
   #                            
   #  # tar_target(topic_number,
   #  #           find_topic_number(topic_model_input),
   #  #             format = "qs") #, 
   #  # tar_target(topic_model,
   #  #            make_topic_model(topic_model_input),
   #  #             format = "qs")

@@

     tar_target(coauthorship_graph,
               make_graph(all_authors))

>>>>

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs"
                            ))

@@

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, final_data)),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector))

@@

   tar_target(topic_model_input,
              make_topic_model_input(all_pubs)),

    tar_target(topic_number,
              find_topic_number(topic_model_input),
                format = "qs"),
    tar_target(topic_model,
               make_topic_model(topic_model_input),
                format = "qs")

@@

     tar_target(coauthorship_graph,
               make_graph(coauthorship))
